---
title: "Lindel_into_R"
author: "Hui Mao"
date: "5/8/2020"
output: html_document
---

# Getting started
* Install and import "reticulate": install.packages("reticulate")
* Python version: By default, reticulate uses the version of Python found on your PATH (i.e. Sys.which("python")).
The use_python() function enables you to specify an alternate version, for example: use_python("/usr/bin/python" )
* use_condaenv() functions enable you to specify versions of Python in virtual or Conda environments.
* Requirements for Lindel with Python: conda install shell
  + Compatible with both Python2.7 and Python3.5 or higher.
  + Requires biopython (Bio),numpy and scipy.
* import: biopython <- import("biopython") or py_run_string('import Bio').

```{r setup}
# install.packages("reticulate")
library(reticulate)
#Set default Python binary.
Sys.setenv(RETICULATE_PYTHON = "/Users/Hui/opt/anaconda3/envs/r-cl/bin/python")
#Suggest a Python binary to use by path.
use_python("/Users/Hui/opt/anaconda3/envs/r-cl/bin/python")
#Suggest a Conda env to use.
use_condaenv("r-cl", conda = "/Users/hui/opt/anaconda3/condabin/conda")
#Check which version of python and packages has been loaded. 
py_config()
Sys.which("python")
py_available()
py_module_available("numpy")
py_module_available("scipy")
py_module_available("Bio")
#import
py_run_string('import scipy')
py_run_string('import numpy')
py_run_string('import Bio')

```


# R_Lindel_prediction
* Define rlindel function based on Lindel_prediction.py, with only one argument: inputseq, return the indels.
* Modificate Lindel_prediction.py with the following:
  + add write_file
  + define rlp (r_lindel_prediction) function.
  + Replace sys.argv[1] with fucntion parameter inputseq.
  + Drop filename = sys.argv[2]
  + Replace print with return.

```{r python}


setwd("/Users/Hui/CRISPRLindel/Lindel")

rlindel<- function(inputseq) {
  source_python("RLindelprediction.py")
  res <- rlp(inputseq)
  e <- 'Error: No PAM sequence is identified.Please check your sequence and try again'
  
  if (res == e) {
   return (e)
  } else {
  res1<- data.frame(res)
  result <- t(res1)
  row.names(result) <- NULL
  colnames(result) <- c("Indels", "Frequency", "Location")
  return(result)
  }
}

#input sequence here
inputseq <- "TAACGTTATCAACGCCTATATTAAAGCGACCGTCGGTTGAACTGCGTGGATCAATGCGTC"

head (rlindel(inputseq))

```


## Enjoy!


